### 2020-04-19 system-model.tex
:pencil: Single-user design

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \text{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \text{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \text{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

@@

	\begin{subsection}{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
		\begin{equation}\label{eq:gamma_{k,n}}
			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta},\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
		\end{equation}
		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the deterministic power component or constructing a translated codebook.
	\end{subsection}

@@

			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta},\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}

@@

					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}h_{k,n}^*(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}

@@

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
			\end{split}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
	\end{subsection}
\end{section}

>>>>

	\begin{subsection}{Composite Channel Model}
		Denote the baseband equivalent channels from the AP to users, from the AP to the IRS, and from the IRS to users as $\boldsymbol{H}_D \in \mathbb{C}^{K \times N}$, $\boldsymbol{H}_I' \in \mathbb{C}^{L \times N}$, and $\boldsymbol{H}_R \in \mathbb{C}^{K \times NL}$ respectively. At subband $n$, the frequency response of direct and reflective links write as $\boldsymbol{h}_{D,n}=[h_{D,1,n},\dots,h_{D,K,n}]^T \in \mathbb{C}^{K \times 1}$ and $\boldsymbol{H}_{R,n}=[\boldsymbol{h}_{R,1,n}^T,\dots,\boldsymbol{h}_{R,K,n}^T]^T \in \mathbb{C}^{K \times L}$ with $\boldsymbol{h}_{R,k,n}=[h_{R,k,n,1},\dots,h_{R,k,n,L}] \in \mathbb{C}^{1 \times L}$. Similarly, the $n$-th incident channel is given by $\boldsymbol{h}_{I,n}=[h_{I,n,1},\dots,h_{I,n,L}]^T \in \mathbb{C}^{L \times 1}$. To decouple the impact of IRS operation on the incident link, we construct a block-diagonal matrix $\boldsymbol{H}_I \triangleq \mathrm{diag}\left\{\boldsymbol{h}_{I,1},\dots,\boldsymbol{h}_{I,N}\right\} \in \mathbb{C}^{NL \times N}$. Element $l$ of the IRS receives a superposed waveform through the multipath channel, then redistributes it by adjusting the amplitude reflection coefficient $\beta_l \in [0,1]$ and phase shift $\theta_l \in [0,2\pi)$. Each passive reflector absorbs a small portion ($1 - \beta_l$) of the signal to support CSI decoding and impedance matching. On top of this, the IRS matrix per subband is constructed by collecting the reflection coefficients onto its diagonal entries as $\boldsymbol{\Theta}_0 = \mathrm{diag}\left\{\beta_1 e^{j \theta_1}, \dots, \beta_L e^{j \theta_L}\right\} \in \mathbb{C}^{L \times L}$. Finally, the IRS matrix is formed by $\boldsymbol{\Theta} = \mathrm{diag}\{\underbrace{\boldsymbol{\Theta}_0,\dots,\boldsymbol{\Theta}_0}_{N\text{ times}}\} \in \mathbb{C}^{NL \times NL}$. The IRS-aided extra link can be modeled as a concatenation of the AP-IRS channel, the IRS reflection matrix, and the IRS-user channel. Both direct and IRS-aided link contributes to the composite channel $\boldsymbol{H} \in \mathbb{C}^{K \times N}$ as
		\begin{equation}\label{eq:H}
			\boldsymbol{H} = \boldsymbol{H}_D+\boldsymbol{H}_R\boldsymbol{\Theta}\boldsymbol{H}_I
		\end{equation}
		whose $(k,n)$-th entry
		\begin{equation}\label{eq:h_{k,n}}
			h_{k,n}=h_{D,k,n}+\boldsymbol{h}_{R,k,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
		represents the overall channel gain of user $k$ at subband $n$. On top of this, the $n$-th subchannel for all users $\boldsymbol{h}_n \in \mathbb{C}^{K \times 1}$ can be expressed as
		% We further define $\boldsymbol{h}_{k,n}=[\underbrace{h_{k,n},\dots,h_{k,n}}_{N\text{ times}}]^T \in \mathbb{C}^{K \times 1}$.s
		\begin{equation}\label{eq:h_n}
			\boldsymbol{h}_n=\boldsymbol{h}_{D,n}+\boldsymbol{H}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}
		\end{equation}
	\end{subsection}

@@

	\begin{subsection}{Information Decoder}
		One major benefit of using proposed waveform is that the deterministic power term $y_{P,k}(t)$ bears no information and creates no interference to the modulated information term $y_{I,k}(t)$. Hence, each user treats the information signals from other users as interference such that the SINR at subband $n$ of user $k$ is
		\begin{equation}\label{eq:gamma_{k,n}}
			\gamma_{k,n}=\frac{(1-\rho)(h_{k,n}w_{I,k,n})(h_{k,n}w_{I,k,n})^*}{\sum_{j=1,j{\ne}k}^K{(1-\rho)(h_{k,n}w_{I,j,n})(h_{k,n}w_{I,j,n})^*+\sigma_n^2}}
		\end{equation}
		where $\sigma_n^2$ is the sum variance of the Gaussian noise at the RF-band and those introduced during the RF-to-BB conversion on subband $n$. Therefore, the achievable rate of user $k$ is expressed as
		\begin{equation}\label{eq:R_k}
			R_k(\boldsymbol{W}_I,\boldsymbol{\Theta}_0,\rho)=\sum_{n=1}^N{\log_2(1+\gamma_{k,n})}
		\end{equation}
		A significant conclusion in \cite{Clerckx2018b} indicates that the rate \ref{eq:R_k} is always achievable with or without waveform cancellation, through either subtracting the determaxistic power component or constructing a translated codebook.
	\end{subsection}

@@

			z_k(\boldsymbol{W}_I,\boldsymbol{W}_P,\boldsymbol{\Theta}_0,\rho)=\sum_{i\,\text{even},i\ge2}^{n_0}{k_i}{\rho^{i/2}}{R_{\text{ant}}^{i/2}}{\mathcal{E}\left\{\mathcal{A}\left\{y_k(t)^i\right\}\right\}}

@@

					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{h_{k,n}^2h_{k,n}^{*2}(\boldsymbol{w}_{I,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{I,n})(\boldsymbol{w}_{P,n}^H\boldsymbol{J}_{K}\boldsymbol{w}_{P,n})}

@@

\begin{section}{Problem Formulation}
	In this section, we first define the weighted sum rate-energy (WSR-E) region then formulate waveform and IRS optimization problems.
	\begin{subsection}{Weighted Sum Rate-Energy Region}
		We define the achievable WSR-E region as
		\begin{equation}
			\begin{split}
				C_{R-I}(P)
				&\triangleq \biggl\{(R,I):R\le\sum_{k=1}^K{u_{I,k}R_k},I\le\sum_{k=1}^K u_{P,k}z_k,\\
				&\quad \frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P}){\le}P\biggr\}
				% &\quad \frac{1}{2}\left(\Vert{\boldsymbol{W}_I}\Vert_F^2+\Vert{\boldsymbol{W}_P}\Vert_F^2\right){\le}P\biggr\}
			\end{split}
		\end{equation}
		where $u_{I,k},u_{P,k}$ denote the information and power weight of user $k$.
	\end{subsection}

	\begin{subsection}{Single-User Optimization}
		In this section, we first characterize the rate-energy region in the single-user setup. Let $h_n={A_n}{e^{j{\bar{\psi}_n}}}$, $w_{I,n}=s_{I,n}e^{j{\phi}_n}$, and $w_{P,n}=s_{P,n}e^{j{\phi}_n}$. Consider the rate maximization problem subject to transmit power and output DC current constraints
		\begin{maxi}
			{\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert^2}{\sigma_n^2}\right)}}{\label{op:1}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{w}_I^H}{\boldsymbol{w}_I}+{\boldsymbol{w}_P^H}{\boldsymbol{w}_P})\le{P}}
			\addConstraint{z(\boldsymbol{w}_I,\boldsymbol{w}_P,\boldsymbol{\Theta}_0,\rho)\ge{\bar{z}}}
			\addConstraint{0\le{\theta_l}\le{2{\pi}},\quad l=1,\dots,L}
		\end{maxi}
		Although the problem is non-convex, the target function can be reformed using the triangle inequality
		\begin{equation}
			\lvert{(h_{D,n}+\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n})w_{I,n}}\rvert \le \lvert{h_{D,n}w_{I,n}}\rvert+\lvert{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}w_{I,n}}\rvert
		\end{equation}
		where the equality holds if and only if the direct and IRS-aided links align with each other. In such case, we have $A_n=A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n}$ and and $\bar{\psi}_n=\angle{h_{D,n}}=\angle{\boldsymbol{h}_{R,n}\boldsymbol{\Theta}_0\boldsymbol{h}_{I,n}}$. Therefore, the optimal phase shift at the $l$-th reflect element is obtained in closed form

		\begin{equation}
			\theta_l^\star=\angle{h_{D,n}}-\angle{h_{R,n,l}}-\angle{h_{I,n,l}}
		\end{equation}
		Besides, it can be concluded from \ref{eq:R_k} and \ref{eq:z_k_standard} that the optimal information and power phases coincide at subband $n$, being matched to composite frequency response as
		\begin{equation}\label{eq:phi_n}
			\phi_{I,n}^\star=\phi_{P,n}^\star=-\bar{\psi}_n
		\end{equation}
		Therefore, \ref{op:1} is transformed to
		\begin{maxi}
			% {\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)(A_{D,n}+\boldsymbol{A}_{R,n}\boldsymbol{A}_{I,n})^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
			{\boldsymbol{s}_I,\boldsymbol{s}_P,\rho}{\sum_{n}{\log_2\left(1+\frac{(1-\rho)A_n^2{s_{I,n}^2}}{\sigma_n^2}\right)}}{\label{op:2}}{}
			\addConstraint{\frac{1}{2}({\boldsymbol{s}_I^H}{\boldsymbol{s}_I}+{\boldsymbol{s}_P^H}{\boldsymbol{s}_P})\le{P}}
			\addConstraint{z(\boldsymbol{s}_I,\boldsymbol{s}_P,\rho)\ge{\bar{z}}}
		\end{maxi}
		with $z$ reduced to \ref{eq:z_gp}.

		\begin{figure*}[b]
			\hrule
			\begin{equation}\label{eq:z_gp}
				\begin{split}
					z
					&=\frac{1}{2}{k_2}{\rho}{R_{\text{ant}}}\sum_n{A_n^2(s_{I,n}^2+s_{P,n}^2)}+\frac{3}{8}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_{\substack{{n_1},{n_2},{n_3},{n_4}\\{n_1}+{n_2}={n_3}+{n_4}}}{A_{n_1}A_{n_2}A_{n_3}A_{n_4}(2s_{I,n_1}s_{I,n_2}s_{I,n_3}s_{I,n_4}+s_{P,n_1}s_{P,n_2}s_{P,n_3}s_{P,n_4})}\\
					&\quad+\frac{3}{2}{k_4}{\rho^2}{R_{\text{ant}}^2}\sum_n{{A_n^4}{s_{I,n}^2}{s_{P,n}^2}}
				\end{split}
			\end{equation}
		\end{figure*}
	\end{subsection}
\end{section}
